Self Regulation Ontology Retest Analyses

### 2018-07-23 code/SRO_Retest_Analyses.Rmd
updated loaded packages

```{r}
summary(lmerTest::lmer(abs(difference) ~ scale(days_btw)+(scale(days_btw) | dv), data=t1_2_difference)) 
```

>>>>

```{r}
#summary(lmerTest::lmer(abs(difference) ~ scale(days_btw)+(scale(days_btw) | dv), data=t1_2_difference))

summary(tmp <- MCMCglmm(abs(difference) ~ scale(days_btw), random = ~us(scale(days_btw)):dv, data=t1_2_difference)) 
```
